\Large \bf One-Step, Three-Factor Authentication With Custom-Fit, In-Ear EEG

### 2017-02-11 paper.tex
small proofs

\underline{Brief outline of the rest of this lit review....}

@@

Custom ear impressions were made by cleaning and injecting silicon into the ear canal. A cotton ball with a string attached is placed into the ear canal first.  When the silicon dries after a few minutes, the string is pulled to remove the impression from the ear canal. This impression is then scanned with a 3D scanner and the resulting scan modified based on some heuristics to achieve a comfortable fit and to ensure the intended electrode sites will make good contact with the skin. Channels are created in the 3d model to allow wire leads and associated EEG electrodes as well as a plastic tube to deliver audio. This 3d model is then sent to a 3d printer. Following this wires leads and associated AGCL electrodes are installed.

>>>>

@@

Custom ear impressions were made by cleaning and injecting silicon into the ear canal. A cotton ball with a string attached is placed into the ear canal first.  When the silicon dries after a few minutes, the string is pulled to remove the impression from the ear canal. This impression is then scanned with a 3D scanner and the resulting scan modified based on some heuristics to achieve a comfortable fit and to ensure the intended electrode sites will make good contact with the skin. Channels are created in the 3D model to allow wire leads and associated EEG electrodes as well as a plastic tube to deliver audio. This 3D model is then sent to a 3D printer. Following this wires leads and associated AGCL electrodes are installed.
